Typed Lua: An Optional Type System for Lua

### 2014-03-13 doc/paper/typedlua.tex
started section on objects

>>>>

Lua's built-in support for object oriented programming is
minimal. The basic mechanism is the {\tt :} syntactic
sugar for method calls and method declarations.
The Lua compiler translates {\tt obj:method(args)}
to an operation that evaluates {\tt obj}, looks
for a field named ``method" in the result, then calls
it with the result of evaluating {\tt obj} as the
first argument, followed by the result of evaluating
the argument list in the original expression.
